---
title: "Example of a Report made in Rmarkdown"
author: "Morten Rasmussen"
date: "February 19 - 2019"
output: 
  html_document:
    toc: true
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'right', fig.width = 10)
```

# Setting libraries

```{r}
library(rio)
library(ggplot2)
```

# Importing Data

First we import data. this can be done in three ways. 

## Relative to current location

```{r}
X <- import('../BASICs/data/cheese_aromas.xlsx')
```

## When the data is in the same folder

```{r, eval=FALSE}
X <- import('cheese_aromas.xlsx')
```

## Hard coded from the root of the PC

```{r}
X <- import('~/Dropbox/Backup/MyDocumentsOnC/Course and teaching/FOOD_Rcourses/BASICs/data/cheese_aromas.xlsx')
```

# A table of data

If we want nice tables in the report, then the two packages knirt and kableExtra is very useful. 

```{r}
library(knitr)
library(kableExtra)
df <- head(X[,1:4],20)
kable(df,digits = 1, caption = 'Some caption for my nice table')

tb <- kable(df,digits = 1) 
tb <- kable_styling(tb, "striped", full_width = F) 
tb <- column_spec(tb, 1:2, bold = T) 
tb <- row_spec(tb, c(7,19), bold = T, color = "white", background = "#D7261E") 
tb <- row_spec(tb, c(3,20), bold = T, color = "white", background = "blue")
tb

```

... Or in the tidyverse way (you'll need tidyverse package installed.)

```{r, eval=FALSE}
library(tidyverse)
kable(df,digits = 1) %>%
  kable_styling("striped", full_width = F) %>%
  column_spec(1:2, bold = T) %>%
  row_spec(c(7,19), bold = T, color = "white", background = "#D7261E") %>% 
  row_spec(c(3,20), bold = T, color = "white", background = "blue")
```

# A nice Plot

We use ggplot2 for plotting the data in an informative way. 

```{r}
ggplot(data = X, aes(time_culture,`1Butanol`, fill = maturation_culture)) + 
  geom_boxplot() + 
  geom_point() + 
  ylab('Response - 1-Butanol') + 
  theme(axis.title=element_text(size=14))

```

# ANOVA of the aromas

After visualization, the data is analysed by ANOVA

```{r}
mdl <- lm(data = X, `1Butanol` ~ maturation_culture*time_weeks)
kable(anova(mdl), digits = 3, caption = 'ANOVA table analysing culture and time interactions')
```

# TOC level 1

## TOC level 2

### TOC level 3

#### TOC level 4

##### TOC level 5

